Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-08-26 response.md

referee response
==========
Major Issue I: Reorganization of Section 4
------------------------------------------
Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the reader.

### 2016-08-26 response.md

referee response
==========
Major Issue I: Reorganization of Section 4
------------------------------------------
Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.

------------------------------------------
Major Issue II: Statistical Model
------------------------------------------
We tested a variety of models for fitting f/f_o, including linear, exponential, polynomial, and power, each testing a constant zeta parameter and a linear with surface brightness dependence. We compared the relative quality of fits using the AIC parameter, and found no great difference in the choice of model ***should quantify this if we can***, the details and code can be viewed in this python notebook (link eventually). Of these, we believe the best model is an exponential fit for f_features vs z with a linear (maybe??) zeta, based on the following:

1)

### 2016-08-26 response.md

referee response
==========
Major Issue I: Reorganization of Section 4
------------------------------------------
Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.

------------------------------------------
Major Issue II: Statistical Model
------------------------------------------

We thank the referee for the very thorough analysis of this method and for the detailed suggestions. We used this input to review and revise the fitting of the ferengi data and construction of the debiasing equation for the Hubble data, as follows:

We tested a variety of models for fitting f/f_o, including linear, exponential, polynomial, and power, each testing a constant zeta parameter and a linear with surface brightness dependence. We compared the relative quality of fits using the AIC parameter, and found no great difference in the choice of model (***should quantify this if we can***), the details and code can be viewed in this python notebook (***link eventually***). Of these, we believe the best model is an exponential fit for f_features vs z with a linear/constant (***need to choose***) zeta, based on the following:

1) While the ferengi data could be fit relatively well using any of the models tested, the exponential is ideal because it is the only form which allows f_features to be simply and continuously bound between 0 and 1, which is a requirement of the debiased vote fractions.

***Zeta: need to choose which.***

2a) We choose a linear equation to represent zeta as a function of surface brightness because (***I can't think of a great reason other than it doesn't hurt since the slope is ~0 anyway, but that feels like such a weak argument...***)

2b) We choose to remove the surface brightness dependence from zeta and use a constant parameter. Between the exponential fit with a constant and linear model for zeta, the constant model was shown to be a slightly better fit via the AIC parameter. We note that this does not change the effect of the debiasing equation strongly, as the original slope was approximately zero. This change is mostly implemented to remove the possible implication that there is any strong surface brightness dependence in the paper.

Additionally, we chose to modify equation 2 to match the normalization of equation 4 (as suggested in minor comment 4).

-----------------------------------
Minor Comment 1
-----------------------------------

-----------------------------------
Minor Comment 2
-----------------------------------

The FERENGI sample is biased to lower surface brightness than the real data, simply because the local Universe does not include galaxies which are as high surface brightness as are found at high redshift. We get around this partially by applying the evolutionary correction described in Section 2.3.2, but this still results in a sample which only spans, not reproduces the surface brightness-redshift distribution of the real data. This is fine as we are not correcting the population as a whole, but only galaxies at a given surface brightness and redshift.

-----------------------------------
Minor Comment 3
-----------------------------------

(*** will continue to be taken care of as section 4 continues to be finalized (pending choice of zeta in Major Comment II), but probable response will be:***)

We have implemented changes in the text that we believe removes the confusion.

-----------------------------------
Minor Comment 4
-----------------------------------

We originally left equation 2 un-bounded because the data being fit was inherently bounded between 0 and 1, while the correction equation 4 would produce vote fractions greater than 1 if left in the same form as 2. We recognize now that the difference in normalization, while being only a small effect on the fitting of the data, is inconsistent and confusing to the reader. Therfore we changed equation 2 to match equation 4 (see response to Major Comment II).

----------------------------------
Minor Comment 5
----------------------------------

This mistake is edited in the text.

---------------------------------
Minor Comment 6
----------------------------------

***response pending final fit / choice of zeta***

----------------------------------
Minor Comment 7
----------------------------------

The regions can be perfectly separated if we keep the discrete binning as in Figure 9 - however we assumed that a true/physical separation would be a smooth function of z-mu-f. Implementing a convex hull in this space created a small amount of contamination around the edges, which was minimized by adjusting the hull as described.

***does this sound efficient?***

----------------------------------
Minor Comment 8
----------------------------------

### 2016-08-29 response.md

The regions can be perfectly separated if we keep the discrete binning as in Figure 9 - however we assumed that a true/physical separation would be a smooth function of z-mu-f. Implementing a convex hull in this space created a small amount of contamination around the edges, which was minimized by adjusting the hull as described.

***does this sound efficient?***

----------------------------------
Minor Comment 8
----------------------------------

We chose to evaluate the distribution of f_features in 5 (not 4, this was a typo) bins to match the common ranges of vote fractions used in GZ morphological studies: 0-0.2 indicating a weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 representing different ranges of intermediate detection, and 0.8-1.0 representing a very strong detection. This explanation has been added to the text.

----------------------------------
Minor Comment 9
----------------------------------
80% was a mostly arbitrary choice to represent the distribution of f_features in a given bin; we discussed and agree with the referee that a more typical statistical range would be more appropriate. We therefore chose to represent the range as the upper and lower 1 sigma limits, or the inner 68% of the data.

----------------------------------
Minor Comment 10
----------------------------------

### 2016-08-30 response.md

-----------------------------------
Minor Comment 2
-----------------------------------

The FERENGI sample is biased to lower surface brightness than the real data, simply because the local Universe does not include galaxies which are as high surface brightness as are found at high redshift. We get around this partially by applying the evolutionary correction described in Section 2.3.2, but this still results in a sample which only spans, not reproduces the surface brightness-redshift distribution of the real data. This is fine as we are not correcting the population as a whole, but only galaxies at a given surface brightness and redshift.

-----------------------------------
Minor Comment 3
-----------------------------------

( ***will continue to be taken care of as section 4 continues to be finalized (pending choice of zeta in Major Comment II), but probable response will be:*** )

@@

----------------------------------
Minor Comment 8
----------------------------------

We chose to evaluate the distribution of f_features in 5 (not 4, this was a typo) bins to match the common ranges of vote fractions used in GZ morphological studies: 0-0.2 indicating a weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 representing different ranges of intermediate detection, and 0.8-1.0 representing a very strong detection. This explanation has been added to the text.

----------------------------------
Minor Comment 9
----------------------------------
80% was a mostly arbitrary choice to represent the distribution of f_features in a given bin; we discussed and agree with the referee that a more typical statistical range would be more appropriate. We therefore chose to represent the range as the upper and lower 1 sigma limits, or the inner 68% of the data.

----------------------------------
Minor Comment 10
----------------------------------
We have switched to a reduced chi squared metric on the grounds that is a more commonly used and typical values are well-known, as suggested by the referee. We believe this metric will make it more evident to the reader that the ferengi data was not well-fit for questions beyond Task 01.

----------------------------------
Minor Comment 11
----------------------------------
Typo has been fixed in the text.

### 2016-09-01 response.md

referee response
==========
Major Issue I: Reorganization of Section 4
------------------------------------------
Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.

------------------------------------------
Major Issue II: Statistical Model
------------------------------------------

We thank the referee for the very thorough analysis of this method and for the detailed suggestions. We used this input to review and revise the fitting of the ferengi data and construction of the debiasing equation for the Hubble data, as follows:

We tested a variety of models for fitting f/f_o, including linear, exponential, polynomial, and power, each testing a constant zeta parameter and a linear with surface brightness dependence. We compared the relative quality of fits using the AIC parameter, and found no great difference in the choice of model. The details and code can be viewed in this python notebook https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb. Of these, we believe the best model is an exponential fit for f_features vs z with a linear zeta, based on the following:

1) While the ferengi data could be fit relatively well using any of the models tested, the exponential is ideal because it is the only form which allows f_features to be simply and continuously bound between 0 and 1, which is a requirement of the debiased vote fractions. Further, the AIC test showed the exponential fit was either better than, or had similar support to the other models tested.

2) We choose a linear equation to represent zeta as a function of surface brightness. In terms of goodness of fit, the AIC test showed both models were of equal quality. While this and the small slope in zeta shows we were not able to detect a surface brightness dependence, we still opt to keep the more general, linear form. As similar debiasing methods are planned for future GZ projects with a greater quantity of ferengi data, in which a possible surface brightness dependence could be better detected, keeping the general form for this project will allow for a closer comparison of the two iterations of the method. We added an emphasis on this reasoning in the paper so as not to lead the readers to the conclusion that we are claiming a strong surface brightness depedence detection in this run.

### 2016-09-01 response.md

referee response
==========
Major Issue I: Reorganization of Section 4
------------------------------------------
Section 4 has been reorganized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.

------------------------------------------
Major Issue II: Statistical Model
------------------------------------------

We thank the referee for the very thorough analysis of this method and for the detailed suggestions. We used this input to review and revise the fitting of the ferengi data and construction of the debiasing equation for the Hubble data, as follows:

We tested a variety of models for fitting f/f_o, including linear, exponential, quadratic, and cubic, each using both a constant zeta parameter and a linear with surface brightness dependence. We compared the relative quality of fits using the AIC parameter, and found no great difference in the choice of model. The details and code can be viewed in this python notebook https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb. Of these, we believe the best model is an exponential fit for f_features vs z with a linear zeta, based on the following:

### 2016-09-02 response.md

----------------------------------
Minor Comment 8
----------------------------------

We chose to evaluate the distribution of f_features in 5 (not 4, this was a typo) bins to match the common ranges of vote fractions used in GZ morphological studies: 0-0.2 indicating a weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 representing different ranges of intermediate detection, and 0.8-1.0 representing a very strong detection. This explanation has been added to the text.

----------------------------------
Minor Comment 9
----------------------------------
80% was a mostly arbitrary choice to represent the distribution of f_features in a given bin; we discussed and agree with the referee that a more typical statistical range would be more appropriate. We therefore chose to represent the range as the upper and lower 1 sigma limits, or the inner 68% of the data.

----------------------------------
Minor Comment 10
----------------------------------
We agree that the normalized chi squared is not the ideal metric for evaluating the goodness of fit here. Rather than comparing the fits of the polynomials for Task 1 vs the rest, we chose to compare the available data per bin. For Task 1, an average of 59 points were fit in each z-mu bin (Figure 9). For the other tasks, an average of 9 points remained in each bin, due to these questions often not being asked of at least 10 users per galaxy, as is required by default in Task 1. We believe this simpler evaluation will make it more evident to the reader that the ferengi data was not well-fit for questions beyond Task 01. Last, we felt that stating these numbers was sufficient and opted to remove the example visual from the appendix.

### 2016-09-06 response.md

referee response
==========
Major Issue I: Reorganization of Section 4
------------------------------------------
Section 4 has been re-organized in the manner suggested by the reviewer. The authors agree this structure will be more clear to the readers.

@@

------------------------------------------
Major Issue II: Statistical Model
------------------------------------------

We thank the referee for the very thorough analysis of this method and for the detailed suggestions. We used this input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:

We tested a variety of models for fitting f/f_o, including linear, quadratic, cubic, and exponential dependences on redshift; for each of these functional forms, we also tested combinations using either a constant zeta parameter or a zeta function that linearly depends on surface brightness. We compared the relative quality of fits using the Akaike information criteria (AIC); for each case, we found no significant differences in the results based on the choice of model. Full details and code for these tests can be viewed in this Python notebook: https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb.

Of all the models tested, we believe the best model is an exponential fit for f_features vs redshift using a linear dependence on zeta. This decision is based on the following points:

1) While the FERENGI data can be fit relatively well using any of the above models, the exponential is ideal because it is the only form which allows f_features to be simply and continuously bound between 0 and 1. This is a key requirement for the debiased votes so that they can be interpreted as normalized fractions. Furthermore, the results of the AIC test show that the exponential fit is either better than, or had similar support to the other models tested.

2) We choose a linear equation to represent zeta as a function of surface brightness. In terms of goodness-of-fit, the AIC test showed both models were of equal quality. While this and the small slope in zeta shows that there is no significant surface brightness dependence in the GZH data, we still opt to keep the more general, linear form. As similar debiasing methods are planned for future GZ projects with a greater quantity of calibration images (and for which there may exist stronger dependencies on surface brightness), keeping the general form for this project will allow for a closer comparison of the two iterations of the method. We have added an emphasis on this reasoning in the manuscript so as not to lead the readers to the conclusion that we are claiming a strong surface brightness depedence detection in this run.

Finally, we have modified Equation 2 to match the normalization of Equation 4 (as suggested in minor comment 4).

@@

-----------------------------------
Minor Comment 1
-----------------------------------

From a strict sense, it is impossible to tell a priori if giving the anonymous classifiers a weight of 1 is valid (since the grouping within the anonymous data is unknown). However, there are large amounts of data from similar projects that support this approach. For the Galaxy Zoo: CANDELS project (Simmons et al. 2016, submitted), which is nearly identical in design to Galaxy Zoo: Hubble and shares a large fraction of the same user base, the distribution of the classifier consistency for both the logged-in and non-logged-in populations peak at the same value (kappa = 0.7). The anonymous users have slightly broader wings, with slightly more addresses at the lowest and highest levels of consistency, but the overall behavior is similar. The roughly 50-50 split between logged-in users and non-logged-in IP addresses is typical of the ratio for Zooniverse crowdsourced projects as a group.

@@

-----------------------------------
Minor Comment 2
-----------------------------------

The FERENGI sample is biased in including examples of galaxies that have lower surface brightnesses than any images found in the real Hubble data, simply because the local Universe has no examples of galaxies at the high surface brightness end. This is a combination of both a finite-volume sample at low redshift in addition to some evolution in the stellar populations and size-magnitude relation over cosmic time.  We deal with this issue partially by applying the evolutionary correction described in Section 2.3.2, but this still results in a sample spans (but does not reproduce) the surface brightness-redshift distribution of the real data. The mismatch does not affect the overall calibration accuracy as we are not correcting the population as a whole, but only galaxies at particular bins of surface brightness and redshift.

@@

-----------------------------------
Minor Comment 3
-----------------------------------

We have implemented changes in the text that we believe removes the confusion.

-----------------------------------
Minor Comment 4
-----------------------------------

We originally left Equation 2 unbounded because the data being fit was inherently bounded between vote fractions of 0 and 1, while the corrected Equation 4 would produce vote fractions greater than 1 if left in the same form as Equation 2. We have realized that the difference in normalization, while having only a small effect on the fitting of the data, is inconsistent and may be confusing to a reader. Therefore, we have changed Equation 2 to match Equation 4 (see response to Major Comment II).

@@

---------------------------------
Minor Comment 6
----------------------------------

***response pending final fit ***

----------------------------------
Minor Comment 7
----------------------------------

The regions in Figure 9 can be perfectly separated in f_features-redshift space if we keep the same discrete binning shown in the figure. However, our analysis makes the assumption that a true/physical separation should be a smooth function of z-mu-f. Implementing a convex hull in this space created a small amount of contamination around the edges, which was minimized by adjusting the hull as described.

@@

***does this sound sufficient?***

----------------------------------
Minor Comment 8
----------------------------------

We chose to evaluate the distribution of f_features in 5 (not 4; a typo in the earlier manuscript has been corrected) bins to match the common ranges of vote fractions used in previous GZ morphological studies: 0.0-0.2 is typically used to indicate weak/no detection of the feature in question, 0.2-0.4, 0.4-0.6, and 0.6-0.8 represent ranges of increasing likelihood of detection, and 0.8-1.0 represents a very strong detection. This explanation and references to other papers using a similar system has been added to the text.

----------------------------------
Minor Comment 9
----------------------------------
The threshold of 80% was a mostly arbitrary choice to represent the distribution of f_features in a given bin; the authors have discussed it and agree with the referee that a more typical statistical range would be more appropriate. We therefore have changed the range to upper and lower 1 sigma limits, or the inner 68% of the data.

----------------------------------
Minor Comment 10
----------------------------------
We agree that the normalized chi-squared is not the ideal metric for evaluating the goodness-of-fit here. Rather than comparing the fits of the polynomials for Task 1 vs the rest of the tasks, we compare the available data per bin. For Task 1, an average of 59 points were fit in each z-mu bin (Figure 9). For the other tasks, an average of 9 points remained in each bin, due to these questions often not being asked of at least 10 users per galaxy (as required by default in Task 1). This simpler evaluation should make it more evident to the reader that the FERENGI data was not well-fit for questions beyond Task 01.

The authors feel that quoting the numbers is sufficient for the manuscript; we have removed the example visual from the Appendix for streamlining.

### 2016-09-06 writeup/gz_hubble_data.tex

We repeated all analyses comparing morphologies between GZH and external
pulblications on the entire GZH dataset, rather than the volume-limited sample
($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the
original magnitude limit of $m<23.5$ are used, the correlations between all of
the automatic morphological populations and GZH decrease significantly.  The
exceptions are the GEMS galaxies, which are the only sample that was visually
classified and had a shallower magnitude cut on their catalogue.  Based on
these comparisons, we suggest that use of morphological catalogues with these
\hst{} images be limited to galaxies with $m_\mathrm{I|i|z}<22.5$; fainter
targets have been demonstrated to be less reliable, regardless of the method of
morphological classification being used.

>>>>

We repeated all analyses comparing morphologies between GZH and external
publications on the entire GZH dataset, rather than the volume-limited sample
($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the
original magnitude limit of $m<23.5$ are used, the correlations between all of
the automatic morphological populations and GZH decrease significantly.  The
exceptions are the GEMS galaxies, which are the only sample that was visually
classified and had a shallower magnitude cut on their catalogue.  Based on
these comparisons, we suggest that use of morphological catalogues with these
\hst{} images be limited to galaxies with $m_\mathrm{I|i|z}<22.5$; fainter
targets have been demonstrated to be less reliable, regardless of the method of
morphological classification being used.
